Title Goes Here

### 2019-03-28 analysis/paper/paper.Rmd
updates for plots

>>>>

```{r get-data, eval = FALSE}
# plot for different shape of agate bead by period
agate_bead_shape <-
  ornaments_period %>% 
  filter(Categories == 'Agate bead') %>% 
  mutate(Type = ifelse(Type == 'prism/octagonal', 
                       str_remove(Type, '/octagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/pentagonal', 
                       str_remove(Type, '/pentagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/hexagonal', 
                       str_remove(Type, 'prism/'), Type)) %>% 
  mutate(Type = fct_infreq(Type)) %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

ggplot(transform(agate_bead_shape,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Agate bead") +
  theme_minimal(base_size = 14)
```

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "dodge")
